A Second Screen Architecture for Capturing Viewers' Interaction Data in TV Environments

### 2014-06-24 src/paper.tex
'Viewers' Identification in iTV' section finished

\subsection{Identification of Viewers in iTV}
\label{ssec_ident_viewers_itv}

The connectivity capabilities of smartphones were used in~\cite{Cabarcos2011}, where the Bluetooth technology was used to detect nearby users.

\cite{Hwang2007}

>>>>

\subsection{Viewers' Identification in iTV}
\label{ssec_ident_viewers_itv}

Since the TV environment can be shared by many viewers (e.g., a family or group of friends), audience identification becomes an important feature for interactive TV systems. Many modern computational systems consist of identifying viewers in order to provide personalized services. Unfortunately, the traditional model of interaction, which uses a conventional remote control, hinders the identification of viewers. The only existing remote control is shared by all viewers and it is difficult to manage who is in possession of the remote control at a given moment.

Some research studies have addressed automated technologies for viewers' identification in interactive TV environments. Cabarcos~\emph{et~al.}~\cite{Cabarcos2011} described an architecture that uses the connectivity capabilities of smartphones to detect viewers nearby the TV terminal at every moment. Each smartphone has a hardware identifier(e.g., the Bluetooth MAC address), which is associated to a viewer identifier according to an association table. Hwang~\emph{et~al.}~\cite{Hwang2007} presented a method based on face recognition to identify viewers in interactive TV environments. The method uses sensors to capture images of the audience and then employs images processing techniques and machine learning algorithm for both detecting and recognizing the faces of the viewers.
